\documentclass[10pt]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{green}

\usepackage[scale=0.75]{geometry}

%%% citations
\usepackage[backend=bibtex,
  style=authoryear,
  sorting=ydnt,
  dashed=false,
  maxbibnames=99]{biblatex}

\renewbibmacro*{date}{}
\renewbibmacro*{date+extrayear}{}
\renewbibmacro*{issue+date}{}
\newcommand*{\bibyear}{}

\defbibenvironment{bibliography}
  {\list
    {\iffieldequals{year}{\bibyear}
      {}
      {\printfield{year}%
       \savefield{year}{\bibyear}}}
    {\setlength{\topsep}{0pt}%
     \setlength{\labelwidth}{0.5\hintscolumnwidth}%
     \setlength{\labelsep}{\separatorcolumnwidth}%
     \setlength{\itemsep}{\bibitemsep}%
     \leftmargin\labelwidth%
     \advance\leftmargin\labelsep}%
     \sloppy\clubpenalty4000\widowpenalty4000}
   {\endlist}
   {\item}

\bibliography{pubs}
%%%

\firstname{Connor}\familyname{Greenwell}
\address{217 Stone Ave., Apt. C}{Lexington, KY 40508}
\phone{(859)351-3405}
\email{cgree3@gmail.com}
\homepage{connorgreenwell.com}
\social[github]{connorgreenwell}

\begin{document}

\makecvtitle

\section{Research Interests}
\cvlistitem{Computer Vision}
\cvlistitem{Deep Learning}
\cvlistitem{Remote Sensing}

\section{Education}
\cventry{Spring 2016 (Exp.)}{B.S. in Computer Science, and Mathematical Science}{University of Kentucky}{Lexington, KY}{3.0}{}

\section{Experience}
\cventry{Summer 2014}{Vialab}{University of North Carolina, Charlotte}{Charlotte, NC}{NSF - Socially Relevant Computing REU}{Worked under Dr.~Richard Souvenir exploring the geo-dependence of facial features in the GeoFaces dataset.}
\cventry{2014 - Date}{Computer Vision Group}{University of Kentucky}{Lexington, KY}{}{Worked under Dr.~Nathan Jacobs on a variety of computer vision research projects.}
\cventry{2013 - 2014}{Software Developer}{Happenstock.com}{Lexington, KY}{}{Developed price scraping, online purchasing and inventory control software.}

\section{Publications}
\nocite{*}
\printbibliography[heading=subbibliography, keyword=journal, title={Peer-Reviewed Journals}]
\printbibliography[heading=subbibliography, keyword=conference, title={Peer-Reviewed Conferences}]
\printbibliography[heading=subbibliography, keyword=workshop, title={Workshops}]
\printbibliography[heading=subbibliography, keyword=review, title={Under Review}]

\section{Talks}
\cventry{Fall 2014}{GeoFaceExplorer}{2014 ACM SIGSPATIAL (GEOCROWD Workshop)}{Dallas, TX}{}{}
\cventry{Summer 2014}{Image Geo-location from Faces}{2014 CISE REU Regional Conference}{Charleston, SC}{Talk and Un-poster Session}{Discussed ways in which visual clues found in peoples faces can assist in geo-locating images.}
\cventry{Spring 2014}{Programming Language Shootout: Go}{CS Dept.
Friday Colloquium: Birds of a Feather}{Lexington, KY}{}{Reviewed Go's benefits as a general purpose/server programming language, as well as its concurrency model.}

\section{Service}
\cventry{Fall 2014}{Organizer}{CS Dept. Friday Colloquium: Birds of a
Feather}{}{}{}
\cventry{Spring 2014}{Organizer}{UK Computer Science Department Awards}{}{}{}
\cventry{Spring 2014}{Volunteer}{IEEE SouteastCon Programming Contest}{}{}{}
\cventry{Spring 2014}{Volunteer}{UK College of Engineering:
E-Day}{}{}{ACM Table: Artificial Intelligence for Playing Board Games;
Microcomputers and CS Education}
\cventry{Fall 2013}{Committee}{ad hoc committee: Virtualization for Instruction}{}{}{Planning the migration from campus computer labs for instruction to virtualized instances accessible over the internet.}
\cventry{Spring 2013}{Volunteer}{UK College of Engineering:
E-Day}{}{}{ACM Table: Physics in Video Games}

\section{Organizations}
\cventry{2014 - 2015}{Vice President}{Association for Computing Machinery, UK Student Chapter}{}{}{}
\cventry{2013 - 2014}{President}{Association for Computing Machinery, UK Student Chapter}{}{}{}
\cventry{2012 - 2013}{Treasurer}{Association for Computing Machinery, UK Student Chapter}{}{}{}
\cventry{2012 - Date}{Member}{IEEE}{}{}{}
\cventry{2011 - Date}{Member}{Association for Computing Machinery}{}{}{}

\section{Relevant Coursework}
\cventry{Spring 2015}{CS 685}{Learning Based Methods for Computer Vision}{Dr.~Nathan Jacobs}{}{}
\cventry{Fall 2014}{CS/MA 416G}{Linear Programming I}{Dr.~Robert Molzon}{}{}
\cventry{Fall 2014}{CS 405G}{Database Systems}{Dr.~Jinze Liu}{}{}
\cventry{Spring 2014}{CS 585}{Assets at Scale}{Dr.~Brent Seales}{}{}
\cventry{Spring 2014}{CS 463G}{Artificial Intelligence}{Tom Allen}{}{}
\cventry{Fall 2013}{CS 485G}{Machine Learning}{Dr.~Nathan Jacobs}{}{}

\end{document}
